A cautionary note on the use of Ornstein Uhlenbeck and other models in macroevolutionary studies

### 2015-04-07 Manuscript/ohyou.tex
Beginning new edits to Biol Linn Soc version

\section{Introduction}
\label{section:introduction} 
%The outcomes of evolutionary processes acting over millions of years can be seen in the distributions and covariances of species traits at the tips of phylogenetic trees. Such processes can be modeled using phylogenetic comparative methods (PCMs). These approaches have been used, for example, to model niche conservatism \citep{Wiens:2010aa}, infer potential rates of species responses to climate change \citep{Quintero:2013aa}, test the role of ecological niche as a driver of morphological evolution \citep{pienaar2013macroevolution}, compare rates of evolution of species traits \citep{Claramunt:2012ab} and test for constraints in adaptive radiations \citep{blackburn2013adaptive}. PCMs are now widely recognized as powerful tools with which to model observed patterns in species traits and potentially to infer the evolutionary processes that drive them \citep[e.g.,][]{freckleton2009seven,Nunn:2011aa,o2012evolutionary,pennell2013integrative}. Despite these advances, the properties of some of the most widely used PCMs are poorly understood leading to the potential for inappropriate use and misinterpretation of results.

%The majority of PCMs use an explicit evolutionary model to characterize trait evolution \citep{Freckleton:2011aa}. A model can be fit using statistical methods (typically maximum likelihood) and model parameters interrogated to test ideas from evolutionary theory. Most model-based methods for characterizing trait evolution are based on the Brownian constant variance model \citep[for exceptions see][]{price1997correlated,harvey2000comparative,freckleton2006detecting}. The Brownian model, first applied in a phylogenetic context by \citet{cavalli1967} and to across-species data by \citet{felsenstein1973maximum}, is a simple model of trait evolution in which trait variance accrues as a linear function of time, and makes the prediction that traits of closely-related species are more similar than those of distantly-related ones. The Brownian model has been modified in various ways to account for a suite of ecological and evolutionary processes (e.g., Grafen 1989; Hansen 1997; Pagel 1997, 1999). Most of these involve a transformation of the tree and thereby fitting a model with one or more extra parameters. These modified Brownian models have become very popular because they fit better, have attractive biological interpretations, and are implemented in freely available packages \citep[e.g., R;][]{R-Core-Team:2014aa}.

One of the most commonly used Brownian-like models is the Ornstein Uhlenbeck (OU) model. This is a modification of the Brownian model with an additional parameter $\alpha$ that measures the strength of return towards a theoretical optimum \citep{hansen1997stabilizing}. The popularity of the OU model has grown exponentially in recent years (Fig. \ref{figure.literature}), in part because these models are now easy to implement apply via packages in R \citep[e.g. ouch, GEIGER and OUwie;][]{Butler:2004aa,Harmon:2008aa,beaulieu2012ouwie}. OU models have become particularly prevalent in ecological studies: 652 papers containing the phrases “Ornstein Uhlenbeck” and “ecology” were published between 2011 and 2013 (Google Scholar search 30th January 2014). Additionally, although they are pattern based, fit to an OU model is now being used as evidence for the action of ecological, or ecologically driven, processes such as phylogenetic niche conservatism, convergent evolution and stabilizing selection \citep[e.g.,][]{Wiens:2010aa,christin2013anatomical,ingram2013surface}.

\begin{figure}
\centering
    \includegraphics[width=10cm, height=10cm, keepaspectratio=true]{Figures/OU_figure1.pdf}
\caption{The number of evolutionary biology (closed circles) and ecology (open circles) papers published between 2005 and 2012 containing the phrase “Ornstein-Uhlenbeck”, as a proportion of the total number of evolutionary biology or ecology papers published that year.}
\label{figure.literature}
\end{figure}

Uses of the Ornstein-Uhlenbeck can be divided into three broad categories that are near equally represented in the literature: (i) modeling the evolution of a continuous character to test for evolutionary constraints or stabilizing selection; (ii) modeling the effects of different hypothesized adaptive regimes on a continuous character and, (iii) controlling for phylogeny in correlative analyses. Here, we focus on the first of these because the principles apply to a range of other macroevolutionary models.

@@

\section{Materials and Methods}
According to the Brownian model \cite{cavalli1967,felsenstein1973maximum}, a trait X evolves at random at a rate $\sigma$:

@@

where $W(t)$ is drawn at random from a normal distribution with mean $0$ and variance $\sigma^2$. The model assumes that there is no overall drift in the direction of evolution (hence the expectation of $W(t)$ is zero) and that the rate of evolution is constant. Because the direction of change in trait values at each step is random, Brownian motion is often described as a ``random walk''. The model assumes the correlation structure among trait values is proportional to the extent of shared ancestry for pairs of species. This means that close relatives will be more similar in their trait values than more distant relatives. It also means that variance in the trait will increase (linearly) in proportion to time. The model has two parameters, the Brownian rate parameter, $\sigma^2$ and the state of the root at time zero, $X(0)$.

@@

The OU model was introduced to population genetics by \cite{Lande:1976aa} to model stabilizing selection in which the mean was recast as a fitness optimum on an adaptive landscape. The process operating in comparative data is analogous, although clearly is not stabilizing selection, despite being sometimes referred to as such (see Discussion).

The variances and covariances predicted by the OU model are more complex than those predicted by the Brownian model. In the light of the results below, some properties of this model are worth highlighting:

  \item If $\alpha$ is small then evolution is approximately Brownian, The question is what is a small value of $\alpha$? Figure \ref{figure.traitsim} provides some guidance on this issue.\\

  \item In the long-term the imprint of history is weakened. If evolution proceeds for a long time the variance in $X_i$ tends to a constant, i.e. because the expected value of $X_i$ is $\mu$. Similarly, in equation (4), the covariance between traits tends to a constant because $T$ becomes large relative to $t_{ij}$. Consequently for large groups the model implies that the imprint of history is weak. As a result adding more species to a phylogeny will contribute only relatively weakly to fitting the model, as the deeper branches within a phylogeny will contribute little information to estimating the parameters.\\

Figure \ref{figure.traitsim} gives some numerical examples, chosen to outline the behavior of $\alpha$ in relation to the above. We show the predicted covariance in traits \ref{equation:OUcov} scaled by the overall variance \ref{equation:OUvar} plotted against the time since divergence, $t_{ij}$ scaled by tree height. Figure \ref{figure.traitsim} highlights that the behavior of $\alpha$ can be classified into three regions. When $\alpha$ is low the model behaves very much like Brownian motion, with the covariance scaling approximately linearly with time. Only as the value becomes moderately larger (in this case approaching a value of $0.5$), does the non-Brownian behavior become apparent. Secondly, there is a region of moderate values in which the model leads to markedly non-Brownian patterns of trait variation (Fig. \ref{figure.traitsim}B).

Finally, when $\alpha$ is large the model behaves differently again: in this case, all imprint of history is lost and the evolution is essentially a rapid burst at the present (Fig. \ref{figure.traitsim}C). This will be indistinguishable from phylogenetically unstructured data.

In terms of statistical model fitting, a feature to highlight is that in Figure \ref{figure.traitsim}A and Figure \ref{figure.traitsim}C, changing the value of α across large relative ranges at the extremes (0-0.5 in Fig. \ref{figure.traitsim}A; 10-50 in Fig. \ref{figure.traitsim}C) produces relatively little quantitative change in the model behavior, and it is in the middle region of parameter space (1-5) that the biggest discernible effects occur.

\subsection{Simulations}
\label{section:sims.methods} 
We used simulations to explore the statistical properties of $\alpha$. We simulated phylogenies with 25, 50, 100, 150, 200, 500, or 1000 tips under pure birth, constant-rate Birth-Death (extinction fractions of 0.25, 0.5 and 0.75), or temporally varying speciation rate (speciation rate modeled as time from the root raised to the power 0.2, 0.5, 2 and 5) models. We simulated 1000 phylogenies for each combination of tips and models resulting in 56,000 simulated phylogenies in total. Trees were simulated using the R package TESS \cite{hohna2013fast}. We then simulated the evolution of a single trait under a Brownian motion model on each phylogeny using the R package MOTMOT \citep{Thomas:2011aa}.  We estimated α and compared the fit of a Brownian model to that of an OU model using: (i) a likelihood ratio test with 1 degree of freedom with the transformPhylo.ML function in MOTMOT; and, (ii) with Bayes factors estimated from a stepping stone sampling procedure \citep{xie2010improving}implemented in BayesTraits. The marginal likelihoods of the models were calculated using a stepping stone sampler in which fifty stones were drawn from a beta distribution with (alpha = 0.4 and beta = 1). Each stone was sampled for 20000 iterations (with the first 5000 iterations discarded). We treated Bayes factors $>$ 2 as evidence favouring the OU model. We used three alternative sets of priors on $\alpha$: (i) an exponential distribution with mean = 1; (ii), an exponential distribution with mean = 10, and (iii) a uniform distribution bounded at 0 and 20. For all analyses we used a uniform -100 to 100 prior for $\mu$ and uniform 0 to 100 for $\sigma^2$. We also normalized the tree length to prevent the $\alpha$ parameter of the OU model from interacting with $\sigma^2$.

@@

We used the same procedure to simulate trait data under a Brownian motion model with known error. Specifically, we simulated trees under a Yule model with 25, 50, 100, 150, 200, 500, or 1000 tips and added branch length of (i) 1\%, (ii) 5\% or (iii) 10\% of the tree height to the tips of the simulated trees. We then simulated data under a Brownian model on each tree. We compared the fit of a Brownian model to that of an OU model (with ML and MCMC stepping stone sampling as above) using the original trees without the addition of extra branch length to the tip edges. The expectation is that the OU model should fit the data better than the Brownian model but the reason for the better fit would be entirely unrelated to any evolutionary process.

Although our focus is on the OU model we also explored three other commonly used models \citep[$\kappa$, $\lambda$, and $\delta$;][]{Pagel:1997aa,Pagel:1999aa} fitted using maximum likelihood using the same simulated data. These models are designed to test for speciational evolution ($\kappa$), strength of phylogenetic signal ($\lambda$) and accelerating or decelerating evolution ($\delta$). The point of these additional tests is to assess the extent to which parameter behaviors vary across models and the results are reported in the supplementary material.

@@

\begin{figure}
  \centering
  \includegraphics[width=10cm, height=10cm, keepaspectratio=true]{Figures/OU_figure3.pdf}
  \caption{Examples of profile likelihoods for selected simulated datasets. In all cases the ‘true’ value of alpha is 0.}
\label{figure.profiles}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=10cm, height=10cm, keepaspectratio=true]{Figures/OU_figure4.pdf}
  \caption{Rejection rates and estimation of $\alpha$ for different tree sizes and shapes. Rejection rates (a,c,e) for the OU model at multiple tree sizes for models fitted using ML (circles) and Bayesian (diamonds) methods. Estimates of $\alpha$ (b,d,f) based on ML (circles show means and dotted lines show 95\% sampling interval from 1000 trees) and Bayesian (diamonds show means and dotted lines show 95\% sampling interval of the modal value from the posterior distribution from 1000 trees).}
\label{figure.rejection}
\end{figure}

Figure \ref{figure.error} shows the proportion of data sets in which the OU model is favoured over the Brownian model for data simulated under Brownian motion with error (also see Figs. S4 and S5). The expectation is that the OU model should fit better because the branch length transformation partially captures the non-Brownian component (the error). There are two points worth noting. First, the frequency with which the OU model is favoured increases with tree size for both ML and Bayesian estimation (Fig. \ref{figure.error}A). With as little as 5\% error, the OU model becomes extremely difficult to reject, even for trees with just 100 species. This is important for the interpretation of the OU model. We cannot conclude anything about evolutionary process from a single optimum OU model unless error is adequately accounted for. Second, for moderate amounts of error (5-10\%), the ML estimates of $\alpha$ are consistently $>$ 1 (Fig. \ref{figure.error}B). Large values of $\alpha$ are similarly difficult to interpret because they are indicative that the signal of the past has been overwritten.

\begin{figure}
  \centering
  \includegraphics[width=10cm, height=10cm, keepaspectratio=true]{Figures/OU_figure5.pdf}
  \caption{Rejection of BM with measurement error (a) and estimation of α (b). Symbols follow Figure \ref{figure.rejection}.}
\label{figure.error}
\end{figure}

@@

\section{Discussion}
\label{section:discussion}
Although it is possible to create and implement new models for comparative data that encompass a range of processes, we have to beware that such models are statistically complex and may behave in unexpected ways. Transformations of the variance-covariance matrix in the Brownian model are an attractive and computationally simple way to modify the basic model to include evolutionary processes. But, as first pointed out by \citet{grafen1989phylogenetic}, the statistical consequences of these modifications can include biases and problems with interpretation. The results we have presented here illustrate that such biases can occur under conditions that closely match the size and type of datasets that are commonly used.

>>>>

\section{Introduction}
\label{section:introduction}

  Phylogenetic comparative methods are powerful tools for identifying patterns in the evolution of species traits, and for potentially inferring the evolutionary processes that underlie them \citep[e.g.,][]{freckleton2009seven,Nunn:2011aa,o2012evolutionary,pennell2013integrative}. 
  These approaches have been used, for example, to model niche conservatism \citep{Wiens:2010aa}, infer potential rates of species responses to climate change \citep{Quintero:2013aa}, test the role of ecological niche as a driver of morphological evolution \citep{pienaar2013macroevolution}, compare rates of evolution of species traits \citep{Claramunt:2012ab} and test for constraints in adaptive radiations \citep{blackburn2013adaptive}. % Maybe cut to three examples?
  %Unfortunately, although widely used, the properties of some phylogenetic comparative methods are poorly understood leading to the potential for inappropriate use and misinterpretation of results.

  Most model-based methods for characterizing trait evolution are based on the Brownian constant variance model \citep[for exceptions see][]{price1997correlated,harvey2000comparative,freckleton2006detecting}. 
  The Brownian model, first applied in a phylogenetic context by \citet{cavalli1967} and to across-species data by \citet{felsenstein1973maximum}, is a simple model of trait evolution in which trait variance accrues as a linear function of time, and makes the prediction that traits of closely-related species are more similar than those of distantly-related ones. 
  The Brownian model has been modified in various ways to account for a suite of ecological and evolutionary processes \citep[e.g.,][]{grafen1989phylogenetic,hansen1997stabilizing,Pagel:1997aa,Pagel:1999aa}. 
  The majority of these involve a transformation of the tree and thereby fitting a model with one or more extra parameters. 
  These modified Brownian models tend to fit better, have attractive biological interpretations, and are implemented in freely available packages \citep[e.g., R;][]{R-Core-Team:2014aa}.

  One of the most commonly used Brownian-like models is the Ornstein Uhlenbeck (OU) model. 
  This is a modification of the Brownian model with an additional parameter $\alpha$ that measures the strength of return towards a theoretical optimum \citep{hansen1997stabilizing}. 
  The OU model was introduced to population genetics by \cite{Lande:1976aa} to model stabilizing selection in which the mean was recast as a fitness optimum on an adaptive landscape. 
  The process operating in comparative data is analogous, although clearly is not stabilizing selection, despite being sometimes referred to as such (see Discussion).

  The popularity of the OU model has grown exponentially in recent years (Fig. \ref{figure.literature}), in part because these models are now easy to implement apply via packages in R \citep[e.g. ouch, GEIGER and OUwie;][]{Butler:2004aa,Harmon:2008aa,beaulieu2012ouwie}. OU models have become particularly prevalent in ecological studies: 652 papers containing the phrases “Ornstein Uhlenbeck” and “ecology” were published between 2011 and 2013 (Google Scholar search 30th January 2014). Additionally, although they are pattern based, fit to an OU model is now being used as evidence for the action of ecological, or ecologically driven, processes such as phylogenetic niche conservatism, convergent evolution and stabilizing selection \citep[e.g.,][]{Wiens:2010aa,christin2013anatomical,ingram2013surface}.

    \begin{figure}
      \centering
      \includegraphics[width=10cm, height=10cm, keepaspectratio=true]{Figures/PapersThruTime.png}
      \caption{The number of evolutionary biology (closed circles) and ecology (open circles) papers published between 2005 and 2012 containing the phrase “Ornstein-Uhlenbeck”, as a proportion of the total number of evolutionary biology or ecology papers published that year.}
      \label{figure.literature}
    \end{figure}

@@

We are not the first to mention these problems, but we hope by
summarising the issues and giving recommendations we can help those
less familiar with the literature.

  \subsection{What is the Ornstein-Uhlenbeck model?}
    According to the Brownian model \cite{cavalli1967,felsenstein1973maximum}, a trait X evolves at random at a rate $\sigma$:

@@

    where $W(t)$ is drawn at random from a normal distribution with mean $0$ and variance $\sigma^2$. 
    The model assumes that there is no overall drift in the direction of evolution (hence the expectation of $W(t)$ is zero) and that the rate of evolution is constant. 
    Because the direction of change in trait values at each step is random, Brownian motion is often described as a ``random walk''.The model assumes the correlation structure among trait values is proportional to the extent of shared ancestry for pairs of species. 
    This means that close relatives will be more similar in their trait values than more distant relatives. It also means that variance in the trait will increase (linearly) in proportion to time. 
    The model has two parameters, the Brownian rate parameter, $\sigma^2$ and the state of the root at time zero, $X(0)$.

@@

%In the light of the results below, some properties of this model are worth highlighting. When $\alpha$ is small, evolution is approximately Brownian, then as $\alpha$ gets larger the non-Brownian behaviour of the model starts to become apparent. Eventually, when $\alpha$ is really large, all imprint of history is lost and the evolution is essentially a rapid burst at the present (Fig. \ref{figure.traitsim}C). This will be indistinguishable from phylogenetically unstructured data.

%Figure \ref{figure.traitsim} gives some numerical examples, chosen to outline the behavior of $\alpha$ in relation to the above. We show the predicted covariance in traits \ref{equation:OUcov} scaled by the overall variance \ref{equation:OUvar} plotted against the time since divergence, $t_{ij}$ scaled by tree height. Figure \ref{figure.traitsim} highlights that the behavior of $\alpha$ can be classified into three regions. When $\alpha$ is low the model behaves very much like Brownian motion, with the covariance scaling approximately linearly with time. Only as the value becomes moderately larger (in this case approaching a value of $0.5$), does the non-Brownian behavior become apparent. Secondly, there is a region of moderate values in which the model leads to markedly non-Brownian patterns of trait variation (Fig. \ref{figure.traitsim}B).

\subsection{What do people use the OU model for?}
Uses of the Ornstein-Uhlenbeck can be divided into three broad categories that are near equally represented in the literature: (i) modeling the evolution of a continuous character to test for evolutionary constraints or stabilizing selection; (ii) modeling the effects of different hypothesized adaptive regimes on a continuous character and, (iii) controlling for phylogeny in correlative analyses. Here, we focus on the first of these because the principles apply to a range of other macroevolutionary models.

\section{Materials and Methods}
  \subsection{Maximum Likelihood simulations}
  \label{section:sims.methods} 
  We used simulations to explore the statistical properties of $\alpha$. 
  We simulated phylogenies with 25, 50, 100, 150, 200, 500, or 1000 tips under pure birth, constant-rate Birth-Death (extinction fractions of 0.25, 0.5 and 0.75), or temporally varying speciation rate (speciation rate modeled as time from the root raised to the power 0.2, 0.5, 2 and 5) models. 
  We simulated 1000 phylogenies for each combination of tips and models resulting in 56,000 simulated phylogenies in total. Trees were simulated using the R package TESS \cite{hohna2013fast}. 
  We then simulated the evolution of a single trait under a Brownian motion model on each phylogeny using the R package MOTMOT \citep{Thomas:2011aa}. 
  We estimated $\alpha$ and compared the fit of a Brownian model to that of an OU model using: (i) a likelihood ratio test with 1 degree of freedom with the \texttt{transformPhylo.ML} function in MOTMOT \citep{Thomas:2011aa}.

\subsection{Effects of measurement error}
  We used the same procedure to simulate trait data under a Brownian motion model with known error. 
  Specifically, we simulated trees under a Yule model with 25, 50, 100, 150, 200, 500, or 1000 tips and added branch length of (i) 1\%, (ii) 5\% or (iii) 10\% of the tree height to the tips of the simulated trees. We then simulated data under a Brownian model on each tree. 
  We compared the fit of a Brownian model to that of an OU model as described above, using the original trees without the addition of extra branch length to the tip edges. 
  The expectation is that the OU model should fit the data better than the Brownian model but the reason for the better fit would be entirely unrelated to any evolutionary process.

\subsection{Bayesian simulations}

and, (ii) with Bayes factors estimated from a stepping stone sampling procedure \citep{xie2010improving}implemented in BayesTraits. The marginal likelihoods of the models were calculated using a stepping stone sampler in which fifty stones were drawn from a beta distribution with (alpha = 0.4 and beta = 1). Each stone was sampled for 20000 iterations (with the first 5000 iterations discarded). We treated Bayes factors $>$ 2 as evidence favouring the OU model. We used three alternative sets of priors on $\alpha$: (i) an exponential distribution with mean = 1; (ii), an exponential distribution with mean = 10, and (iii) a uniform distribution bounded at 0 and 20. For all analyses we used a uniform -100 to 100 prior for $\mu$ and uniform 0 to 100 for $\sigma^2$. We also normalized the tree length to prevent the $\alpha$ parameter of the OU model from interacting with $\sigma^2$.

@@

\subsection{Other models}
Although our focus is on the OU model we also explored three other commonly used models \citep[$\kappa$, $\lambda$, and $\delta$;][]{Pagel:1997aa,Pagel:1999aa} fitted using maximum likelihood using the same simulated data. These models are designed to test for speciational evolution ($\kappa$), strength of phylogenetic signal ($\lambda$) and accelerating or decelerating evolution ($\delta$). The point of these additional tests is to assess the extent to which parameter behaviors vary across models and the results are reported in the supplementary material.

@@

%\begin{figure}
 % \centering
  %\includegraphics[width=10cm, height=10cm, keepaspectratio=true]{Figures/OU_figure3.pdf}
  %\caption{Examples of profile likelihoods for selected simulated datasets. In all cases the ‘true’ value of alpha is 0.}
%\label{figure.profiles}
%\end{figure}

@@

%\begin{figure}
  %\centering
  %\includegraphics[width=10cm, height=10cm, keepaspectratio=true]{Figures/OU_figure4.pdf}
  %\caption{Rejection rates and estimation of $\alpha$ for different tree sizes and shapes. Rejection rates (a,c,e) for the OU model at multiple tree sizes for models fitted using ML (circles) and Bayesian (diamonds) methods. Estimates of $\alpha$ (b,d,f) based on ML (circles show means and dotted lines show 95\% sampling interval from 1000 trees) and Bayesian (diamonds show means and dotted lines show 95\% sampling interval of the modal value from the posterior distribution from 1000 trees).}
%\label{figure.rejection}
%\end{figure}

%Figure \ref{figure.error} shows the proportion of data sets in which the OU model is favoured over the Brownian model for data simulated under Brownian motion with error (also see Figs. S4 and S5). The expectation is that the OU model should fit better because the branch length transformation partially captures the non-Brownian component (the error). There are two points worth noting. First, the frequency with which the OU model is favoured increases with tree size for both ML and Bayesian estimation (Fig. \ref{figure.error}A). With as little as 5\% error, the OU model becomes extremely difficult to reject, even for trees with just 100 species. This is important for the interpretation of the OU model. We cannot conclude anything about evolutionary process from a single optimum OU model unless error is adequately accounted for. Second, for moderate amounts of error (5-10\%), the ML estimates of $\alpha$ are consistently $>$ 1 (Fig. \ref{figure.error}B). Large values of $\alpha$ are similarly difficult to interpret because they are indicative that the signal of the past has been overwritten.

%\begin{figure}
 % \centering
  %\includegraphics[width=10cm, height=10cm, keepaspectratio=true]{Figures/OU_figure5.pdf}
  %\caption{Rejection of BM with measurement error (a) and estimation of α (b). Symbols follow Figure \ref{figure.rejection}.}
%\label{figure.error}
%\end{figure}

@@

\section{Discussion}
\label{section:discussion}

Recommendations

Interpreting results
 - OU is favoured over BM. If alpha is small it's basically BM. What
is alpha? Talk about half lives.
 - Not stabilising selection
 - Not an issue if you're just mopping up error structure for PGLS (?)
 - If really want to be certain OU over BM you need 200 species
 - Account for measurement error

Although it is possible to create and implement new models for comparative data that encompass a range of processes, we have to beware that such models are statistically complex and may behave in unexpected ways. Transformations of the variance-covariance matrix in the Brownian model are an attractive and computationally simple way to modify the basic model to include evolutionary processes. But, as first pointed out by \citet{grafen1989phylogenetic}, the statistical consequences of these modifications can include biases and problems with interpretation. The results we have presented here illustrate that such biases can occur under conditions that closely match the size and type of datasets that are commonly used.
